Data Exploration: IUCN and AquaMaps

### 2016-08-17 data_explore/data_explore.Rmd
updated spp inclusion breakdown to be ordered by number of species

taxa_df2 <- taxa_all_df %>%
  bind_rows(taxa_all_df %>%
              mutate(class = ' ',
                     start = 0,
                     end   = 0,
                     n_total = NA)) %>%
  bind_rows(taxa_df1 %>%
              select(-IUCN, -AquaMaps, -Paired)) %>%
  mutate(class = factor(class, levels = unique(.$class), ordered = TRUE),
         n_label = ifelse(!is.na(n_total), paste0('n = ', n_total), ''),
         dataset = factor(dataset, levels = c('AquaMaps', 'Paired', 'IUCN'), ordered = TRUE))

@@

bar_taxa <- ggplot(taxa_df2, aes(x = class, color = dataset)) +
  ggtheme_plot + 
  theme(panel.grid.major.x = element_blank()) +
  geom_linerange(aes(ymin = start, ymax = end, size = dataset),
                 position = position_dodge(width = 0.5)) +
  scale_size_manual(values = c('IUCN' = .25, 'AquaMaps' = .25, 'Paired' = 2.5)) +
  scale_color_manual(values = c('IUCN' = 'black', 'AquaMaps' = 'grey60', 'Paired' = 'black')) +
  geom_text(aes(label = n_label, y = 102),
            size = 2,
            angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 130),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) +
  labs(x = 'Class',
       y = 'Percent of mapped species',
       fill = 'Dataset')

>>>>

taxa_df2 <- taxa_all_df %>%
  bind_rows(taxa_all_df %>%
              mutate(class = ' ',
                     start = 0,
                     end   = 0,
                     n_total = NA)) %>%
  bind_rows(taxa_df1 %>%
              select(-IUCN, -AquaMaps, -Paired) %>%
              arrange(desc(n_total))) %>%
  mutate(class = factor(class, levels = unique(.$class), ordered = TRUE),
         n_label = ifelse(!is.na(n_total), paste0('n = ', n_total), ''),
         dataset = factor(dataset, levels = c('AquaMaps', 'Paired', 'IUCN'), ordered = TRUE))

@@

bar_taxa <- ggplot(taxa_df2, aes(x = class, color = dataset)) +
  ggtheme_plot + 
  theme(panel.grid.major.x = element_blank()) +
  geom_linerange(aes(ymin = start, ymax = end, size = dataset),
                 position = position_dodge(width = 0.5)) +
  scale_size_manual(values = c('IUCN' = .25, 'AquaMaps' = .25, 'Paired' = 2.5)) +
  scale_color_manual(values = c('IUCN' = 'black', 'AquaMaps' = 'grey60', 'Paired' = 'black')) +
  geom_text(aes(label = n_label, y = 102),
            size = 2,
            angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 130),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) +
  labs(x = 'Class (in order of decreasing number of included species)',
       y = 'Percent of mapped species',
       fill = 'Dataset')
